### 2021-05-03 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

Not for this work, we will add to future work.
Also, building a comparison baseline that integrates all that functionality
is very ad-hoc, and would complicate the understanding of the origins
of the benefits of VDMS.

We can provide appendix.

\bigskip
\textbf{
D2 (W1): All queries involve “resize” operation, which is expensive for the
baselines since it is happening on the client side.
A simplistic query without resizing can show how the graph model performs
against traditional RDS DBs (i.e., will show that VDMS has comparable
performance even for such use-case without "visual manipulation").
}\bigskip

This is a great point, we very much appreciate the suggestion.
We have run a new experiment and added a new figure to the paper (Figure 9),
where we compare 3 of the queries with and without the resize operation
to compare the results.
We have also added an explanation on the differences in performance
in the final version.

@@

\bigskip
\textbf{
D1. The proposed solution seems to use the functionalities of the existing systems
as it is. Authors should provide more original ideas or more innovative designs.
For example, providing optimizations that specifically target visual data or query
patterns associated could have been more meaningful to the research communities and
convince users to replace their customized solution to VDMS.
}\bigskip

We partially address this in D3 and also elaborated more on the benefits of
using VDMS over relational databases in Section 3.1.

\bigskip
\textbf{
D2. Both baselines are similar in architecture, and the evaluation has not effectively
highlighted the performance gain of other design choices authors made in VDMS,
except that the VDMS server process both metadata operation and image operation
within only one round of communication with clients.
For example, benchmarking systems can be built to test in isolation the
improvement on metadata handling.
}\bigskip

Thank you for the input. To demonstrate the benefits of VDMS more clearly,
we have added Figure 9 which compares queries with and without the resize operation.
Without the resize operation, the evaluation demonstrates the
improvement on metadata handling better.

@@

\bigskip
\textbf{
D3. The paper should detail the types of queries, and image preprocessing it supports,
as this being “one of the most differentiating aspects” as mentioned by them.
And for the selection of operations supported, authors need to argue for their
decision in the application contexts.
}\bigskip

Thank you for this recommendation.
We have provided additional details on which operations we support and our
decision for chosing the operations in section 3.

\bigskip
\textbf{
D4. Data scientists commonly perform data exploration on raw data and interactively
curate their datasets for downstream tasks like model training.
VDMS could design new mechanisms to support interactive analysis,
which would be beneficial.
}\bigskip

Interactive analysis is out of scope for this paper but this can easily be done
using the current implementation of VDMS.
To support interactive analysis, a new API/frontend could be implemented on top of
VDMS as a webservice without adding any additional abstractions.
An example of such frontend can be found <http://coco.datasets.aperturedata.io>.

### 2021-05-03 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

Not for this work, we will add to future work.
Also, building a comparison baseline that integrates all that functionality
is very ad-hoc, and would complicate the understanding of the origins
of the benefits of VDMS.

We can provide appendix.

\bigskip
\textbf{
D2 (W1): All queries involve “resize” operation, which is expensive for the
baselines since it is happening on the client side.
A simplistic query without resizing can show how the graph model performs
against traditional RDS DBs (i.e., will show that VDMS has comparable
performance even for such use-case without "visual manipulation").
}\bigskip

This is a great point, we very much appreciate the suggestion.
We have run a new experiment and added a new figure to the paper (Figure 9),
where we compare 3 of the queries with and without the resize operation
to understand the difference in performance better.
We have also added an explanation on these differences in performance
in the final version.
Note that, even if the resize happens on the client side in the case of both
baselines we have built, the computing capabilities of the server and the
client are identical. This is on purpose, to avoid the difference in
computing power for the resize operation to affect the understanding
of the results.

@@

\bigskip
\textbf{
D1. The proposed solution seems to use the functionalities of the existing systems
as it is. Authors should provide more original ideas or more innovative designs.
For example, providing optimizations that specifically target visual data or query
patterns associated could have been more meaningful to the research communities and
convince users to replace their customized solution to VDMS.
}\bigskip

We partially address this in D3 and also elaborated more on the benefits of
using VDMS over relational databases in Section 3.1.

\bigskip
\textbf{
D2. Both baselines are similar in architecture, and the evaluation has not effectively
highlighted the performance gain of other design choices authors made in VDMS,
except that the VDMS server process both metadata operation and image operation
within only one round of communication with clients.
For example, benchmarking systems can be built to test in isolation the
improvement on metadata handling.
}\bigskip

Thank you for the input. To demonstrate the benefits of VDMS more clearly,
we have added Figure 9, which compares queries with and without the resize operation.
Without the resize operation, the evaluation demonstrates the
improvement on metadata handling better, plus the effect of a single round
of communication between client and the server (as it is the case with VDMS).

@@

\bigskip
\textbf{
D3. The paper should detail the types of queries, and image preprocessing it supports,
as this being “one of the most differentiating aspects” as mentioned by them.
And for the selection of operations supported, authors need to argue for their
decision in the application contexts.
}\bigskip

Thank you for this recommendation.
We have provided additional details on which operations we support and our
decision for choosing the operations in section 3.

@@

\bigskip
\textbf{
D4. Data scientists commonly perform data exploration on raw data and interactively
curate their datasets for downstream tasks like model training.
VDMS could design new mechanisms to support interactive analysis,
which would be beneficial.
}\bigskip

Interactive analysis is out of scope for this paper but this can easily be done
using the current implementation of VDMS.
To support interactive analysis, a new API/frontend could be implemented on top of
VDMS as a web app without adding any additional abstractions.
An example of such front-end can be found <http://coco.datasets.aperturedata.io>.
The front-end is very thin, as most of the heavy-load is done by VDMS through
the interfaces mentioned in this work
(plus a thin REST abstraction we have added recently).

### 2021-05-04 yfcc100m/paper/vldb2021/submision/review_response/reviews_response.tex

Thank you for the input. To demonstrate the benefits of VDMS more clearly,
we have added Figure 9, which compares queries with and without the resize operation.
Without the resize operation, the evaluation demonstrates the
improvement on metadata handling better, plus the effect of a single round
of communication between client and the server (as it is the case with VDMS).

\bigskip
\noindent %
\textbf{
D3. The paper should detail the types of queries, and image preprocessing it supports,
as this being “one of the most differentiating aspects” as mentioned by them.
And for the selection of operations supported, authors need to argue for their
decision in the application contexts.
}\bigskip

Thank you for this recommendation.
We have provided additional details on which operations we support and our
decision for choosing the operations in section 3.

\bigskip
\noindent %
\textbf{
D4. Data scientists commonly perform data exploration on raw data and interactively
curate their datasets for downstream tasks like model training.
VDMS could design new mechanisms to support interactive analysis,
which would be beneficial.
}\bigskip

Interactive analysis is out of scope for this paper but this can easily be done
using the current implementation of VDMS.
To support interactive analysis, a new API/front-end could be implemented on top of
VDMS as a web app without adding any additional abstractions.
An example of such front-end can be found \url{http://coco.datasets.aperturedata.io}.
The front-end is very thin, as most of the heavy-load is done by VDMS through
the interfaces mentioned in this work
(plus a thin REST abstraction we have added recently).

\bigskip
\noindent %
\textbf{
D5. In terms of scalability, the paper only shows that VDMS can handle large
datasets, yet it is not known how VDMS can scale horizontally with more
computation resources.
For more complex logic of image preprocessing, VDMS will suffer from its
single server capacity.
}\bigskip

@@

Thanks for this comment, we have added a "Future Work" section where the need
for this capability in a distributed version of VDMS.

\newpage
\section{Reviewer \#5}

\noindent %
\textbf{
D1: VDMS is a valuable contribution to Database systems where it takes
some first important steps to handle visual data as a first-class citizen
instead of considering it a blob of information. However, the description
of VDMS is rather short (only 4 pages), and some critical technical
details are missing. In particular, what are the technical challenges
for supporting ACID properties using the graph model abstraction? Are
the solutions analogous to RDBMS’s? Does VDMS also support crash
recovery like an RDBMS? What are the key challenges for implementing
the new visual object computations?
}\bigskip

Thank you for the comment.
We have expanded portions of the VDMS description where necessary.
In Section 3.2, we have expanded on the crash recovery of PMGD in
comparison to other graph databases.

\bigskip
\noindent %
\textbf{
D2: The coverage of persistent memory is underwhelming because persistent memory
is never used in the experiments.
What is the key advantage of using persistent memory and how is it
more suitable for visual data? Why not add experiments comparing VDMS with
and without using PMGD?
}\bigskip

@@

Due to page limitations and the use of SSDs instead of persistent memory in the
evaluation, we did not elaborate on advantages of PMGD and related experiments.

\bigskip
\noindent %
\textbf{
D3: The experiments section seems unnecessarily long, yet missing some important
details. All the experiments are performed on images and do not handle videos or feature
values at all. For example, video operations may include interval operations or video
clip retrieval. Some parts seem redundant, e.g., the description of Figure 9 seems
near-identical to that of Figure 8.
}\bigskip

The paper is focused on an image search application so we did not include any
experiments on videos or feature vectors. We have experiments that we can provide in
appendix but due to page limitations, it did not fit the scope of this paper.

Figure 8 and 9 are quite similar but provide the performance difference with different
number of concurrent clients. We have removed figure 9 and replaced with a figure
demonstrating the difference between queries with and without the resize operation.

\bigskip
\noindent %
\textbf{
D4: There are some minor typos.\\
Page 1: “need for multiple system”\textrightarrow “need for multiple systems”\\
Page 5: “desing specifically”\textrightarrow “designed specifically”\\
Page 7: “images, taglist, and taglist”\textrightarrow “images, taglist, and autotags”\\
Page 10, Figure 6: “10M database).”\textrightarrow “10M database”
}\bigskip

### 2021-05-04 yfcc100m/paper/vldb2021/submission/review_response/reviews_response.tex

\bigskip
\noindent %
\textbf{
D3: The experiments section seems unnecessarily long, yet missing some important
details. All the experiments are performed on images and do not handle videos or feature
values at all. For example, video operations may include interval operations or video
clip retrieval. Some parts seem redundant, e.g., the description of Figure 9 seems
near-identical to that of Figure 8.
}\bigskip

The paper is focused on an image search application so we did not include any
experiments on videos or feature vectors. We have experiments that we can provide in
appendix but due to page limitations, it did not fit the scope of this paper.

Figure 8 and 9 are quite similar but provide the performance difference with different
number of concurrent clients. We have removed figure 9 and replaced with a figure
demonstrating the difference between queries with and without the resize operation.

\bigskip
\noindent %
\textbf{
D4: There are some minor typos.\\
Page 1: “need for multiple system” $\rightarrow$  “need for multiple systems”\\
Page 5: “desing specifically” $\rightarrow$ “designed specifically”\\
Page 7: “images, taglist, and taglist” $\rightarrow$ “images, taglist, and autotags”\\
Page 10, Figure 6: “10M database).” $\rightarrow$ “10M database”
}\bigskip

### 2021-05-04 yfcc100m/paper/vldb2021/design.tex
Corrected spelling and minor updates to design

VDMS provides a \textit{graph model} abstraction with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
This is, users interact with their objects (metadata, images, videos, etc),
as if these objects were in a connected graph.
Graph represents an easier abstraction to model complex problems,
making it very suitable for the data and access patterns shown by visual metadata,
which can be easily mapped into application-level abstractions by
developers~\cite{tao}.
For instance, abstractions like \textit{BoundingBoxes} associated to
images or videos can be easily represented using nodes and edges in a graph.
This is the main reason why the team chose a graph model over a
relational one for the implementation of VDMS API.

VDMS API provides a mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The information associated to each visual object (image, video, etc) is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve these objects based on its properties.
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
retrieval time. This is one of the main differentiating aspects when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model supports (tables, columns).
This is, a SQL query can retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc).

@@

Figure \ref{fig:arch} depicts the high-level architecture of VDMS, which
is composed by several subcomponents, and a Query Engine that implements
the unified API and hides all the complexity underneath.
We first describe the VDMS API, and then describe its subcomponents
and design decisions.

@@

One of the most important differentiating aspects of VDMS is its API.
VDMS is unique in recognizing visual entities (i.e., images, videos, etc)
as first class citizens.
Thus, VDMS' API revolves around visual data operations and retrieval,
but at the same time, enables applications to store any other
application-specific metadata.
VDMS API is easy to use and explicitly pre-defines certain
primitives associated with metadata, images, videos, and feature vectors.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based API,
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between expressiveness
(compared to well-established query languages like SPARQL, Gremlim, or even SQL)
and the ability to natively support visual data operations.
However, we believe it is possible for our API to achieve similar levels of
expressiveness compared to more mature query languages over time.

@@

The Graph Engine used in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
In cases where the system may crash or fail, PMGD has the ability
to recover to a consistent state without loading its content into memory.
Unlike existing graph databases that are disk-based, our graph engine
avoids converting data from a disk-friendly format to an usable format for an application.
PMGD comes as a C++ library that VDMS uses for implementing its query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
PMGD performance evaluation will be published separately.

@@

The Visual Compute Module was designed and implemented to provide
an internal abstraction layer for interacting with visual data.
It enables the query engines to coordinate and perform
visual data handling and processing
(i.e., basic building block operations like crop, resize, etc for images/videos
and k-nearest neighbor search for feature vectors),
shown in Figure \ref{fig:arch}.
For traditional formats (jpg, png, tiff, mp4, etc.),
the interface is an abstraction layer over OpenCV.
However, it also provides a way to use novel formats that are
better suited for visual analytics: a novel, array-based lossless image format.
This format is built on the array data manager TileDB~\cite{TileDB} and
is well suited for images that are used in visual analytics.
Note that, even if VDMS currently provides support for array-based lossless
image format, we do not use it as part of this evaluation.
This work focuses on a more direct comparison with a combination of alternatives,
and thus we use the traditional format (jpg and png).
The performance comparison between the array-based lossless image format
we develop and other similar formats (like png or tiff) are outside of the
scope of this evaluation.

>>>>

VDMS provides a \textit{graph model} abstraction with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
This is, users interact with their objects (metadata, images, videos, etc.),
as if these objects were in a connected graph.
Graph represents an easier abstraction to model complex problems,
making it very suitable for the data and access patterns shown by visual metadata,
which can be easily mapped into application-level abstractions by
developers~\cite{tao}.
For instance, abstractions like \textit{BoundingBoxes} associated to
images or videos can be easily represented using nodes and edges in a graph.
This is the main reason why the team chose a graph model over a
relational one for the implementation of VDMS API.

VDMS API provides a mechanism to insert and connect Images, Videos, BoundingBoxes,
Frames, and Descriptors (feature vectors), together with any metadata
associated with the objects.
Each object is a node in the graph.
The information associated to each visual object (image, video, etc.) is modeled as
"properties" of the node in the graph.
Users can query, filter, and retrieve these objects based on its properties.
VDMS does not simply treat these objects as binary blobs of data, but rather
understands them and the type of processing that is common for them,
providing the ability to run processing on-the-fly, both at insertion and
retrieval time. This is one of the main differentiating aspects when compared to other
database systems, including relational databases.
In a relational database, for instance, one can query \textit{and compute}
over values in a column only for basic data types (strings, integers, floats),
and over the abstractions the relational model supports (tables, columns).
This is, a SQL query can retrieve the \textit{computed average} "salary" of all
the employees in a company (stored using the table/columns abstraction),
but cannot perform any computation over data stored as a blob or binary object.
VDMS, because it recognized the nature of visual objects by design,
provides the ability to \textit{compute} on these visual objects
(image, videos, etc.).

@@

Figure \ref{fig:arch} depicts the high-level architecture of VDMS, which
is composed by several sub-components, and a Query Engine that implements
the unified API and hides all the complexity underneath.
We first describe the VDMS API, and then describe its sub-components
and design decisions.

@@

One of the most important differentiating aspects of VDMS is its API.
VDMS is unique in recognizing visual entities (i.e., images, videos, etc.)
as first class citizens.
Thus, VDMS' API revolves around visual data operations and retrieval,
but at the same time, enables applications to store any other
application-specific metadata.
VDMS API is easy to use and explicitly pre-defines certain
primitives associated with metadata, images, videos, and feature vectors.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based API,
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between expressiveness
(compared to well-established query languages like SPARQL, Gremlim, or even SQL)
and the ability to natively support visual data operations.
However, we believe it is possible for our API to achieve similar levels of
expressiveness compared to more mature query languages over time.

@@

The Graph Engine used in VDMS is the
\textit{Persistent Memory Graph Database} (PMGD).
PMGD was developed at Intel Labs, and was designed and optimized for
persistent memory technologies like Intel Optane~\cite{IntelXPoint15}, which
promise storage providing nearly the speed of DRAM and the
durability of block-oriented storage.
PMGD is also fully open-sourced \footnote{https://github.com/IntelLabs/pmgd}.
PMGD implements an in-persistent-memory graph database optimized
to run on a platform equipped with persistent memory, but
also provides the option to run on SSD and ext4 filesystem
using OS support to provide transactional guarantees (through \textit{msync}).
PMGD provides a property graph model of data storage with the traditional
atomicity, consistency, isolation, and durability
(ACID) properties expected from databases.
Specifically, the database remains consistent, each transaction either
completes entirely or not at all, and the effects of a completed transaction
survives any failure.
In cases where the system may crash or fail, PMGD has the ability
to recover to a consistent state without loading its content into memory.
Unlike existing graph databases that are disk-based, our graph engine
avoids converting data from a disk-friendly format to an usable format for an application.
PMGD comes as a C++ library that VDMS uses for implementing its query engine.
Because PMGD already supports most of the graph abstractions we wanted
to see on VDMS API, it was our preferred option.
Also, our internal evaluation shows that PMGD is faster
than other graph databases, including Neo4j\cite{miller2013graph}.
In this paper, the evaluation uses SSDs instead of persistent memory.
Hence, PMGD performance evaluation will be published separately to highlight
the advantages of using persistent memory for visual data.

@@

The Visual Compute Module was designed and implemented to provide
an internal abstraction layer for interacting with visual data.
It enables the query engines to coordinate and perform
visual data handling and processing
(i.e., basic building block operations like crop, resize, etc. for images/videos
and k-nearest neighbor search for feature vectors),
shown in Figure \ref{fig:arch}.
For traditional formats (jpg, png, tiff, mp4, etc.),
the interface is an abstraction layer over OpenCV.
However, it also provides a way to use novel formats that are
better suited for visual analytics: a novel, array-based lossless image format.
This format is built on the array data manager TileDB~\cite{TileDB} and
is well suited for images that are used in visual analytics.
Note that, even if VDMS currently provides support for array-based lossless
image format, we do not use it as part of this evaluation.
This work focuses on a more direct comparison with a combination of alternatives,
and thus we use the traditional format (jpg and png).
The performance comparison between the array-based lossless image format
we developed and other similar formats (like png or tiff) are outside of the
scope of this evaluation.
